---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
<!-- badges: start -->
  [![Travis build status](https://travis-ci.com/tanaylab/tgutil.svg?branch=master)](https://travis-ci.org/tanaylab/tgutil)
  <!-- badges: end -->

# tgutil package - Tanay's group collection of simple utility functions #


## Read legacy csv's

### fread_rownames ###

```{r, eval=FALSE}
fread_rownames(..., row.var='rowname')
```

Use `fread()` to read a csv/tsv with row names (e.g. one created with `read.table()`). The name of the column that will hold the row names is given in `row.var`.

All arguments are passed to the underlying `fread()` call. Note that the following arguments can't be used (and will be silently ignored): `header`, `skip`, `col.names`.


## Sparse Matrix I/O ##

### fwrite_mm ###

```{r, eval=FALSE}
fwrite_mm(x, fname, sep=' ', row.names=TRUE, col.names=TRUE)
```

Write the contents of the sparse matrix `x` into the text file `fname` in the MatrixMarket format (see http://math.nist.gov/MatrixMarket/formats.html).

The MatrixMarket format does not save row and column names. `fwrite_mm()` allows saving them into separate files using the `row.names` and `col.names` arguments. These arguments may contain file names into which the column and row names will be written. Alternately setting these arguments to `TRUE` will cause the row and column names to be written to `<fname>.rownames` and `<fname>.colnames` respectively.

The argument `sep` indicates the field separator that will be used. Note that using any field separator other than space will result in an output that is not compliant with the MatrixMarket format.

### fread_mm ###

```{r, eval=FALSE}
fread_mm(fname, sep=' ', row.names=TRUE, col.names=TRUE)
```

Reads a sparse matrix in the MatrixMarket format from the file `fname`.

The MatrixMarket format does not save row and column names. `fread_mm()` allows reading them from separate files using the `row.names` and `col.names` arguments. These arguments may contain file names from which the column and row names will be read. Alternately setting these arguments to `TRUE` will cause the row and column names to be read from `<fname>.rownames` and `<fname>.colnames` respectively.

